Brownian motion of main-belt asteroids on human timescales

### 2025-02-17 main.tex
More on impulse distribution

@@

The two largest asteroids, Ceres and Vesta, have masses determined to
high precision by the \textit{Dawn} spacecraft.  Thus despite holding
most of the mass of the MBAs, their $\sigma_M$ values are just ??? and
the unknown part of their contributions to other MBA's motion are
quite small.  Aside from a handful of other asteroids in
well-characterized binary systems, most other knowledge of MBA masses
comes from mutual gravitational encounters.
\citet{negin} forecast the extent to which LSST data will be able to
constrain the masses of individual MBAs by measuring deflections of
the $\approx 10$ tracer asteroids they encounter most closely over the
course of the nominal 10-year survey.  They find that the $1\sigma$
statistical error on a typical MBA is $\sigma_M=???\, M_\odot.$

@@

\begin{figure}
  \includegraphics{mbacounts.pdf}
  \caption{Differential counts of MBAs cataloged by the MPC are
    plotted vs absolute magnitude $H$  
    for the Inner, Middle, Outer, and ``Other'' regions of
    the main belt, and for their total.  We assume that they are
    complete for $H\le17,$ and extrapolate to fainter sources using
    the functional form from \eqq{eq:lsstmba} shown as the dotted
    curve.}
  \label{fig:counts}
\end{figure}

@@

\subsubsection{Individually detectable impulses}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{isq.pdf}
  \caption{Each panel shows statistics of the encounters between
    tracer MBAs from one region and deflector MBAs from another.  As a
    function of the relative velocity at impact, the three curves show
    the mean squared value of the radial, azimuthal, and vertical
    components of the impulse direction $\bhat.$  The horizontal
    dashed line at value $1/3$ would be the result for isotropic
    encounters, but we see that the azimuthal component of the impulse
    tends to be larger, with a variety of behaviors.  The gray regions
    trace the distribution $dN/dv$ of the rate of interactions per
    tracer per orbit per interval in $v.$  These curves have a common
    (arbitrary) normalization, so the relative heights properly
    reflect the frequency of encounters between different MBA
    regions.}
  \label{fig:rtz}
\end{figure}

@@

The two largest asteroids, Ceres and Vesta, have masses determined to
high precision by the \textit{Dawn} spacecraft.  Thus despite holding
most of the mass of the MBAs, their $\sigma_M$ values are just
$\approx3\times10^{-15} M_\odot$ and
the unknown part of their contributions to other MBA's motion are
quite small.  Aside from a handful of other asteroids in
well-characterized binary systems or visited by spacecraft, most other knowledge of MBA masses
comes from mutual gravitational encounters.
\citet{negin} forecast the extent to which LSST data will be able to
constrain the masses of individual MBAs by measuring deflections of
the $\approx 10$ tracer asteroids they encounter most closely over the
course of the nominal 10-year survey.  They find that the $1\sigma$
statistical error on a typical MBA is $\sigma_M=???\, M_\odot.$

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{mbacounts.pdf}
  \caption{Differential counts of MBAs cataloged by the MPC are
    plotted vs absolute magnitude $H$  
    for the Inner, Middle, Outer, and ``Other'' regions of
    the main belt, and for their total.  We assume that they are
    complete for $H\le17,$ and extrapolate to fainter sources using
    the functional form from \eqq{eq:lsstmba} shown as the dotted
    curve.}
  \label{fig:counts}
\end{figure}

@@

\subsubsection{Individually detectable impulses}
For several \citet{negin} forecast the uncertainty $\sigma_v$ on the impulse 
applied to each $\approx7000$ tracers using astrometric data expected from LSST
over its 10-year duration.  The value of $\sigma_I$ depends upon the
apparent magnitude of the tracer, the timing and geometry of the
impulse, and the stochastic variations in the observing pattern and
weather for LSST.
For impulses occurring near the midpoint
of the survey, $\approx80\%$ of all cases yield $\sigma_I<10^{-4}\,{\rm m}\,{\rm
  s}^{-1},$ some an order of magnitude lower.  We conservatively
assume that $I_{\rm det}=5\times 10^{-4}\,{\rm m}\,{\rm
  s}^{-1},$ which when normalized by $v_c$ yields $I_{\rm
  det}=10^{-8}$ at 10\% accuracy across the main belt.
